Differentially Private Bayesian Inference

### 2018-06-19 main.tex
update titles

\subsection{Accuracy Study}
In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kind of sensitivity and the Laplace mechanism.

\subsubsection{Accuracy Study Based on Hellinger Distance}
\label{subsec_accuracy_hellinger}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}
We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.

@@

\subsubsection{Accuracy Study Based on $L_1$ Norm}
\label{subsec_accuracy_l1}
In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig. \ref{fig_dirichlet_hellinger_l1}.

@@

\subsection{Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study in Sec. \ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the relationship between Laplace mechanism and our exponential mechanism. We will do analysis both in theory and experiment based on accuracy bound and probability formula, and then study on some concrete cases.

>>>>

\subsection{Experimental Evaluations on Accuracy}
In this section, we do some experiments in order to study the accuracy property of these mechanisms, including the exponential mechanism with three kind of sensitivity and the Laplace mechanism.

\subsubsection{Based on Hellinger Distance}
\label{subsec_accuracy_hellinger}
% \begin{figure*}
% \begin{center}
% \centering
%   \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
%   \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
%     \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
% \caption{The experimental results of accuracy of four algorithms}
% \label{fig_data}
% \end{center}
% \end{figure*}
We first analyzed the accuracy based on the Hellinger distance. By repeating the experiments for 10000 times and plotting the accuracy after each execution, we got two groups of results under different parameters setting as in Fig. \ref{fig_beta_hellinger} and Fig. \ref{fig_dirichlet_hellinger}. X-axis is labeled with different mechanisms. We took four mechanisms in our experiments: our newly designed exponential mechanism with smooth sensitivity named ``ExpoMech of SS'', exponential mechanism with local sensitivity named `` ExpoMech of LS'', exponential mechanism with global sensitivity named `` ExpoMech of GS'' and Laplace mechanism named ``LaplaceMech''. Y-axis is the accuracy measured by Hellinger distance between output $r$ of each execution and the correct inference result $\bysinfer(x)$, $\hlg(r, \bysinfer(x))$.

@@

\subsubsection{Based on $L_1$ Norm}
\label{subsec_accuracy_l1}
In this section, we will study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$ for comparison, as in Fig. \ref{fig_dirichlet_hellinger_l1}.

@@

\subsection{Evaluations on Accuracy Trade-off Between Laplace and Our Exponential Mechanism with Smooth Sensitivity}
\label{subsec_accuracy_tradeoff}
Based on accuracy study in Sec. \ref{subsec_accuracy_hellinger} and \ref{subsec_accuracy_l1}, we are going to have a further study on the relationship between Laplace mechanism and our exponential mechanism. We will do analysis both in theory and experiment based on accuracy bound and probability formula, and then study on some concrete cases.
